---
title: "Vignettes"
author: "Sylvia Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial distribution}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(ggplot2)
library(binomial)
```

# Binomial Distribution
## The package `"binomial"` is an R package that implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.


# bin_variable() initiates a binomial variable 
## Given number of trials and probability, we can generate a binomial variable. 
```{r}
bin_var <- bin_variable(trials=10, prob=0.5)
bin_var
```


# summary() provides a summary of the given binomial variable
## Given a binomial variable, we can get the summary about it
```{r}
bin_sum <- summary(bin_var)
bin_sum
```


# Binomial Functions
## bin_choose() calculates the number of combinations in which k successes can occur in n trials
```{r}
bin_choose(n = 10, k = 4)
```


## bin_probability() calculates the probability of certain successes in certain trials with certain probability
```{r}
bin_probability(success = 3, trials = 6, prob = 0.5)
```


## bin_distribution() creates a dataframe for the probability of each successes with certain probability and trials
## plot() presents a plot to visualize the binomial distribution
```{r}
dis1 <- bin_distribution(trials = 10, prob = 0.5)
dis1
plot(dis1)
```


## bin_cumulative() creates a dataframe for cumulative probability of each successes certain with probability and trials
## plot() presents a plot to visualize the binomial distribution
```{r}
dis2 <- bin_cumulative(trials = 10, prob = 0.5)
dis2
plot(dis2)
```


## Functions of Measurement
## the following functions calculate important statistic measurements of the binomial distribution
```{r}
#mean
bin_mean(trials = 10, prob = 0.5)
#variance
bin_variance(trials = 10, prob = 0.5)
#mode
bin_mode(trials = 10, prob =0.5)
#skewness
bin_skewness(trials = 10, prob = 0.5)
#kurtosis
bin_kurtosis(trials = 10, prob = 0.5)
```

